Untitled

### 2024-10-03 code/manuscript_altanalysis.Rmd
better measures, geographic piece too

```{r}
dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
#uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
#  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense)

@@

df.zip <- df.zip %>% 
  left_join(df.zip.totals, by = c("ZipCode","ReportingYear")) %>% 
  group_by(BHCMISID, GrantNumber, ReportingYear) %>% 
  summarise(MS_num = sum(NumberofPatients, na.rm = TRUE), 
            MS_denom = sum(Totals, na.rm = TRUE)) %>% 
  mutate(MS = 100 - (MS_num / MS_denom * 100))

@@

df.temptemp <- df.mt %>% 
  rename(ID = ID.x) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
  select(value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Complexity, Intensity, Pct.None:Pct.COM, CostPerPat, Altman, Staff) %>% 
  unique()

df.temptemp <- df.temptemp %>% 
  group_by(ID) %>% 
  mutate(value_min = min(value, na.rm = TRUE), value_max = max(value, na.rm = TRUE), value_last = last(value, na_rm = TRUE), value_first = first(value, na_rm = TRUE)) %>% 
  mutate(Tx = value - value_min) %>% 
  filter(value_min == value_max | value_last > value_first)

@@

for (k in 1:10){

  df.temptemptemp <- df.temptemp
  colnames(df.temptemptemp)[(13+k)] <- "Outcome"
  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | I(MS/10) ~ value + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)

@@

}
data.frame(cbind(colnames(df.temptemp)[14:23], (coeffs[-1,])))

@@

df.temptemptemp <- df.temptemp %>% select(Qcomp, MS, value, Year, ID, Pct.NHA:Pct.COM) %>% ungroup() %>% filter(complete.cases(.))

reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
firststage <- lm(data = df.temptemptemp, I(MS/10) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )

model <- lm(data = df.temptemptemp, Qcomp ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless)
summary(model)

@@

>>>>

```{r}
#dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
#uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
#  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / ngla_expense * 100, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets * 100, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense)

@@

df.zip.HHI <- df.zip %>% 
  group_by(BHCMISID, ReportingYear, ZipCode) %>% 
  summarise(ZipTotal = sum(NumberofPatients)) %>% 
  left_join(df.zip.totals, by = c("ReportingYear","ZipCode")) %>% 
  mutate(MS = ZipTotal / Totals * 100) %>% 
  ungroup() %>% 
  arrange(ZipCode, ReportingYear) %>% 
  group_by(ZipCode, ReportingYear) %>% 
  mutate(ZipHHI = sum(MS ^2)) %>% 
  group_by(BHCMISID, ReportingYear) %>% 
  mutate(ClinicTotal = sum(ZipTotal), 
         ClinicHHI = sum(ZipHHI * ZipTotal / ClinicTotal)) %>% 
  arrange(BHCMISID, ReportingYear, ZipCode)

df.zip <- df.zip %>% 
  left_join(df.zip.totals, by = c("ZipCode","ReportingYear")) %>% 
  group_by(BHCMISID, GrantNumber, ReportingYear) %>% 
  summarise(MS_num = sum(NumberofPatients, na.rm = TRUE), 
            MS_denom = sum(Totals, na.rm = TRUE)) %>% 
  mutate(MS = 100 - (MS_num / MS_denom * 100)) %>% 
  left_join(df.zip.HHI %>% select(BHCMISID, ReportingYear, ClinicHHI) %>% unique(), by = c("BHCMISID","ReportingYear"))

@@

df.temptemp <- df.mt %>% 
  rename(ID = ID.x) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, 
         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, ngla_revenue, ngla_expense, Profitability, LiabPctAssets, Staff) %>% 
  unique()

## htn.total, dm.total, pap.denom, crc.denom, childbmi.denom, adultbmi.denom

df.temptemp <- df.temptemp %>% 
  group_by(ID) %>% 
  mutate(value_min = min(value, na.rm = TRUE), value_max = max(value, na.rm = TRUE), value_last = last(value, na_rm = TRUE), value_first = first(value, na_rm = TRUE)) %>% 
  mutate(Tx = value - value_min) %>%

  filter(value_min == value_max | value_last > value_first) %>% 
  mutate(value = ifelse(value >= 6, 6, value))

# %>% 
#   group_by(ID) %>% 
#   mutate(Strata = min(Profitability, na.rm = TRUE)) %>% 
#   filter(Strata < 0)

@@

for (k in 1:21){

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)

@@

}

core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:37], (coeffs[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`)

core.iv.estimates <- core.iv.estimates
rownames(core.iv.estimates) <- NULL

core.iv.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 3, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))

## First Stage DID Estimates

```{r}
 did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))  , 
      yname = "ClinicHHI", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

## First Stage DID Event Study
```{r}

 event_study(data = df.temptemp ,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 5) %>%
  #filter(estimator == "Gardner (2021)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.COM) %>% ungroup() %>% filter(complete.cases(.))

reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
firststage <- lm(data = df.temptemptemp, I((10000 - ClinicHHI)/1000) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )

model <- lm(data = df.temptemptemp, Qcomp ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless)

m1coeffs_cl <- coeftest(model, vcov = vcovCL, cluster = ~ID)
m1coeffs_cl

@@

## Why are the signs funky? 
We are likely picking up shifting trends in the level differences across values.

```{r}
df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
  mutate(value = ifelse(value >= 6, 6, value)) %>% 
  group_by(value, Year) %>% 
  summarise(MS = mean(MS, na.rm = TRUE)) %>% 
  ggplot(aes(x = Year, y = MS, group = value, color = as.factor(value))) + geom_point() + geom_line()
```

## Balance between treated and controls
```{r}

df.temptemp %>% 
  filter(Year == 2012) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Staff) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

##  Trends over time, figure 1

```{r}
## Plot
p <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>%
  group_by(`BHCMIS ID`, Year) %>%
  summarise(Clinics = max(Clinics, na.rm = TRUE)) %>%
  group_by(Year, Clinics) %>% 
  summarise(Count = n()) %>% 
  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
  group_by(Year, CompetitorsInArea) %>% 
  summarise(Count = sum(Count)) %>% 
  filter(CompetitorsInArea != "-Inf")

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))), 
          method = list("last.points", hjust = 1, vjust = c(2, 2.5, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
  geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

p.desc <- ggarrange(plot1, plot0, ncol = 1)

p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))

#ggsave(filename = "Figure1.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p.desc, width = 8, height = 11)

# p.desc <- ggarrange(plot1, plot0, ncol = 2) 
# 
# p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))

#ggsave(filename = "Picture1h.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)

p.desc

## Changes in geographic distribution of resources by Distance to competitive zip

## Treatment vs control, only in zip code of interest
df.z <- left_join(df.temptemp, 
                  #uds.zip %>% mutate(Zip = `ZipCode`) %>% select(`BHCMISID`, Zip) %>% unique() , by = c("BHCMIS ID" = "BHCMISID")) %>%
                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>% filter(Year %in% c(2010:2023)) %>% select(`BHCMIS ID`, Zip) %>% unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
  left_join(uds.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear", "Zip" = "ZipCode")) %>%

  ungroup() %>% 
  ###### MAJOR CHANGE: remove those CHCS wtih missing market share MS from GrantNumber
 #filter(!is.na(`MS`)) %>% 
  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
  rename(ID.chc = ID) %>% 
  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z) %>%
  arrange(`BHCMIS ID`, Zip, Year) %>% 
  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)

length(unique(df.z$ID))

df.z <- df.z %>% 
  left_join(df.z %>%
            filter(Tx.z == 1) %>%
            group_by(ID, Zip) %>%
            summarise(Att.z = min(Year)), by = c("ID", "Zip")) %>%
  mutate(Att.z = ifelse(is.na(Att.z), 0, Att.z)) #%>%
# inner_join(df.z %>% filter(!is.na(Clinics)) %>% group_by(ID) %>% summarise(n()) %>% filter(`n()` == length(unique(df.qual.exp$Year))), by = c("ID")) #%>% filter(Att == Att.z)

length(unique(df.z$ID))

df.z <- df.z %>% 
    left_join(uds.sites.full %>% 
              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
              #filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year, Zip) %>% 
              summarise(Sites = n(), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)), by = c("BHCMIS ID","Year", "Zip")) %>% 
  mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar))

df.z <- df.z %>% 
  left_join(df.zip.totals, by = c("Zip" = "ZipCode","Year" = "ReportingYear")) %>% 
  mutate(MS = 100 - (NumberofPatients / Totals * 100)) %>% 
  left_join(df.zip.HHI, by = c("BHCMIS ID" = "BHCMISID","Year" = "ReportingYear","Zip" = "ZipCode"))

df.z

## Spatial Analysis

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year)

coeffs <- c(0,0,0,0, 0, 0, 0, 0)

for (k in 1:8){

  df.z.temp2 <- df.z.temp
  colnames(df.z.temp2)[k] <- "Outcome"
  model <-  did2s(
      data = df.z.temp2, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  + I(Tx * DirectlyTreated),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs <- rbind(coeffs, c(model$coeftable[2,], model$coeftable[1,]))

}

zip.estimates <- data.frame(cbind(colnames(df.z.temp)[1:8], (coeffs[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Estimate.1, `95% CI.1`)

zip.estimates <- zip.estimates[c(1, 6, 2:5, 7:8),]
rownames(zip.estimates) <- NULL

zip.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 2, "Patient and Payer Mix" = 4, "Access" = 2)) %>% 
  add_header_above(c(" " = 1, "Directly Competitive" = 2, "Indirectly Competitive" = 2)) %>% 
  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Zip Codes in Incumbent Clinics' Service Area" = 5))
